Hierarchical Dispatching and Overriding

### 2017-09-30 NewVersion/sections/Formalization.tex
Early Sections in Section 3

\section{Formalization}~\label{sec:formalization}
In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) , based on
Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules, and small-step semantics are presented below.

@@

The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a method named $m$ with result type $I$, parameters $\overline{x}$ of type $\overline{I_x}$ and the overriding target $J$. The body of the method is the single statement $ \kwreturn \; e;$. We also allow defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is similar as normal method but without a method body. Notebly, We have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''; otherwise
it is hierarchical overriding.
For simplicity, overloading is not modelled for methods, which
implies we can uniquely identify a method by its name.

@@

Details of type-checking rules are displayed at the bottom of Figure~\ref{fig:typingrules}, including expression
typing, well-formedness of methods and interfaces. As a convention, an environment
$\Gamma$ is maintained to store the types of variables, together with ``this'' type, namely
the enclosing type. The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
are very similar, in the sense that they all check the type of the specific method, by using
an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
illustrate later in Section~\ref{subsec:auxdefs}. After the method type is obtained, they all check that arguments and the receiver
have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

@@

Finally, \textsc{(T-Invk)} defines interface checking. The condition helps to ensure unambiguity and type soundness of the calculus. We will
introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
in any case. The interface check is responsible for capturing ambiguity during compilation.

\begin{figure*}[t]
\saveSpaceFig
\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	% \tsuperinvk \\
	% \tstaticinvk  \\
	\tnew \\
	\tmethod \\
	\tabsmethod \\
	\tintf \\
	\tanno
\end{mathpar}
\label{fig:typingrules}
\saveSpaceFig
\end{figure*}

>>>>

\section{Formalization}~\label{sec:formalization}
In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), based on
Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules,
small-step semantics and type soundness proofs are presented.

@@

The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
method named $m$ with result type $I$, parameters $\overline{x}$ of
type $\overline{I_x}$ and the overriding target $J$. The body of the
method is the single statement $ \kwreturn \; e;$. We also allow
defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is
similar to a normal method but without a method body. Notably, we have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''; otherwise
it is hierarchical overriding.
For simplicity, overloading is not modelled for methods, which
implies we can uniquely identify a method by its name.

@@

Details of type-checking rules are displayed at the bottom of Figure~\ref{fig:typingrules}, including expression
typing, well-formedness of methods and interfaces. As a convention, an environment
$\Gamma$ is maintained to store the types of variables, together with
the ``this'' type, namely
the enclosing type. The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
are very similar, in the sense that they all check the type of the specific method, by using
an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
illustrate later in Section~\ref{subsec:auxdefs}. After the method
type is obtained, they all check that the arguments and the receiver
have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

@@

Finally, \textsc{(T-Intf)} defines interface checking. The
condition\bruno{Well, there are two conditions. I suggest you explain
  in a bit more detail the 2 conditions, since this rule seems to be
  the more complex one. Some examples may help.} helps to ensure unambiguity and type soundness of the calculus. We will
introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
in any case. The interface check is responsible for capturing ambiguity during compilation.

\bruno{Explanation for T-Anno is missing}

\begin{figure*}
\saveSpaceFig
\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	% \tsuperinvk \\
	% \tstaticinvk  \\
	\tnew \\
	\tmethod \\
	\tabsmethod \\
	\tintf \\
	\tanno
\end{mathpar}
\label{fig:typingrules}
\saveSpaceFig
\caption{Typing and subtyping of \name{}.}
\end{figure*}
